---
title             : "Somthing about Telework?"
shorttitle        : "Super-Dissertation"

author: 
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1 Normal Ave. Dickson Hall #226, Montclair, NJ"
    email         : "garciaprier1@montclair.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Montclair State University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  
keywords          : "keywords"
wordcount         : "X"


bibliography      : ["r-references.bib", "remote.bib", "Dissertation.bib"]


floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Introduction

## Introduction of topic 
+ Prior to the 2020 Pandemic, telework was an increasingly common practice in the    U.S, with about ___% of the U.S workforce engaging in remote work at least part    of the time. 
+ How much telework is used prior to pandemic
+ How much it is used now (after the pandemic) 
+ Despite it being offered, reasons why people might not make use of it              (visibility, social isolation, career mobility, culture or manager negative views   of telework)
+ Telework as a tool to help employees’ work-life balance 
+ Mixed findings of outcomes of telework and non-linear relationships such as for    autonomy/control and intensity 
+ Identify the gap in the literature and research I will be addressing 

## In-depth discussion about each construct 
+ Telework 
    + Theories to explore it 


The term telecommuting was first introduced in the 1970’s by Jack Nilles, an engineer for the National Aeronautics and Space Administration (Berthiaume, 2020) and the director of interdisciplinary research at University of South California. He suggested the use of satellite offices closer to employees’ homes as a way to avoid traffic congestion, pollution, and gas emissions.  Additionally, he claimed telecommuting could potentially lead to decreased levels of stress for employees, and increased productivity (Berthiaume, 2020). Research on the feasibility of this new work arrangement was soon after funded by the federal government, and by 1997, 10,000 federal government employees were working from remote locations [@avery_flexible_2001]. Remote work arrangements later on began to be used by private organizations to address issues with the workforce such as talent sourcing, and as a resource to help employees balance work and family demands [@avery_flexible_2001]. Advancements in technology facilitated the use of remote work arrangements, especially in the 1980s with the introduction of personalized computers, and in the 1990s with laptops and cellphones [@allen_how_2015]. Another contributing factor to the expanding use of remote work was the increase in knowledge-based jobs, which lend themselves to remote work. 

There were two main acts of legislature that enabled organizations to use remote work arrangements in the late twentieth century. In the 1990’s major revisions to The Clean Air Act (1970) were carried out, which further drove the establishment of remote work arrangements. The Clean Air Act requires states to develop enforceable plans to achieve and maintain air-quality standards. The changes done in the 90s required employers to develop employee commute option programs, the possibility to telecommute could satisfy this requirement [@us_epa_1990_2015]. The second important act of legislature that contributed to the prevalence of remote work was the Americans with Disabilities Act (ADA) in 1990. The ADA required employers to make reasonable accommodations for employees with disabilities, and providing remote work arrangements had the potential to fulfill those requirements (U.S Equal Employment Opportunity Commission, 2003). 

# Research Question and Review Topic

Remote worker wellbeing and effectiveness and how this relates to work-nonwork balance and experiencing social isolation.
+ I think we could easily tie this into the JD-R theory and it's probably broad enough for the review (comps). 

Constructs to consider:
+ Work-nonwork balance
+ Social Isolation
+ Use of technology
+ Remote work effectiveness
+ Individual perspective on: demands and resources as well as work and nonwork balance?

# Things to consider for Review: 

+ interdisciplinary take encompassing other fields and journals
+ Chronological order (pre-covid and post-covid)
+ Perceptions on how X factors of work have changed due to the drastic transition to remote work


# NOTES: 

+ "Data from these surveys
suggest that in 2014, 59% of U.S. employers allowed for
some form of telecommuting. More specifically, 54% of
respondents indicated that their organizations offered
telecommuting on an ad hoc basis (i.e., intermittently
throughout the year or as a one-time event), 29% on a
part-time basis, and 20% on a full-time basis (Society for
Human Resources Management, 2014)" - Allen & Shockley (2015)

+ This will change drastically after the 2020 pandemic in which __% of the population was suddenly forced to engage in remote work, and organizations had to adapt within a matter of months to this work arrangement. Some companies had moved away from remote work practices (examples from GOM paper), while others implemented remote work for the first time. 

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
 
@biron_when_2016

# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

# Timeline


```{r Spring2021, echo=FALSE, warning=FALSE}
# Forms for Dissertation found here: 
##https://www.montclair.edu/graduate/current-students/doctoral-students/


## https://www.rdocumentation.org/packages/TeachingDemos/versions/2.10/topics/cal

library(TeachingDemos)

## Colors in 8 digit hex: https://www.quackit.com/css/color/values/css_hex_color_notation_8_digits.cfm


setday <- cal(1,2021) 
setday <- cal(2,2021)
setday(1)
text(0.5,0.5,"Dissertation\nCommittee")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(28)
text(0.5,0.5,"Review topic\nto share w/committee")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")


setday <- cal(3,2021)                               
setday <- cal(4,2021)
setday(1)
text(0.5,0.5,"Proposal outline\nand reading list")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <- cal(5,2021)
setday(31)
text(0.5,0.5,"Comp proposal \n& Reading list")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(6,2021)
setday(30)
text(0.5,0.5, "Out of Money")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday <-cal(7,2021)

setday <-cal(8,2021)

setday(1)
text(0.5,0.5,"10p proposal")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(30)
text(0.5,0.5,"Comp\nExams")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(9,2021)
setday(1)
text(0.5,0.5,"Have proposal\nready")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(14)
text(0.5,0.5,"Written Comp")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")


setday(25)
text(0.5,0.5,"Proposal approval\nform to\nGradschool")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(10,2021)
setday(14)
text(0.5,0.5,"Oral defense")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(11,2021)
setday <-cal(12,2021)

```


```{r Spring2022, echo=FALSE, warning=FALSE}

setday <-cal(1,2022)

setday <-cal(2,2022)

setday <-cal(3,2022)
setday(1)
text(0.5,0.5,"Defense date\nsubmitted to\nGradschool")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday <-cal(4,2022)
setday(1)
text(0.5,0.5,"Defend dissertation\nby this date")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday(2)
text(0.5,0.5,"Submit Approval\nto Gradschool")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(5,2022)

```

